\vspace{2cm} \Large \bf Seasonal influenza circulation patterns and future projections

### 2016-02-19 auspice/reports/tex/feb-2016.tex
Update TeX and include figure legends. Fixes #130.

% text layout
\usepackage{geometry}
\geometry{textwidth=16.5cm} % 15.25cm for single-space, 16.25cm for double-space
\geometry{textheight=22.5cm} % 22cm for single-space, 22.5cm for double-space

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H3N2_counts.png}
	\caption{\textbf{Sample counts through time and across regions.} 
	}
	\label{H3N2_counts}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H3N2_clades.png}
	\caption{\textbf{Frequency trajectories of H3N2 clades.} 
	}
	\label{H3N2_clades}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.9\textwidth]{../figures/feb-2016/H3N2_3c2a_tree.png}
	\caption{\textbf{H3N2 / 3c2.a phylogeny colored by genotype.} 
	}
	\label{H3N2_3c2a_tree}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H3N2_mutations.png}
	\caption{\textbf{Frequency trajectories of 3c2.a subclades.} 
	}
	\label{H3N2_mutations}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H3N2_HI.png}
	\caption{\textbf{H3N2 phylogeny colored by antigenicity.} 
	}
	\label{H3N2_HI}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H3N2_basal_viruses.png}
	\caption{\textbf{Viruses basal to the (HA1:171K, HA2:77V/155E) clade (left panel) and to the HA1:142K/197R/168V clade (right panel).} 
	}
	\label{H3N2_basal_viruses}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H1N1pdm_counts.png}
	\caption{\textbf{Sample counts through time and across regions.} 
	}
	\label{H1N1pdm_counts}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.9\textwidth]{../figures/feb-2016/H1N1pdm_tree.png}
	\caption{\textbf{H1N1pdm phylogeny colored by genotype.} 
	}
	\label{H1N1pdm_tree}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H1N1pdm_mutations.png}
	\caption{\textbf{Frequency trajectories of H1N1pdm variants.} 
	}
	\label{H1N1pdm_mutations}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H1N1pdm_6b2_tree.png}
	\caption{\textbf{H1N1pdm phylogeny showing clade 6b.2 viruses colored by sampling location.} 
	}
	\label{H1N1pdm_6b2_tree}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H1N1pdm_HI.png}
	\caption{\textbf{H1N1pdm phylogeny colored by antigenicity.} 
	}
	\label{H1N1pdm_HI}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Vic_mutations.png}
	\caption{\textbf{Frequency trajectories of B/Vic variants.} 
	}
	\label{Vic_mutations}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Yam_clades.png}
	\caption{\textbf{Frequency trajectories of B/Yam clades.} 
	}
	\label{Yam_clades}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Yam_mutations.png}
	\caption{\textbf{Frequency trajectories of B/Yam variants.} 
	}
	\label{Yam_mutations}
\end{figure}

>>>>

% text layout
\usepackage{geometry}
\geometry{textwidth=16.75cm} % 15.25cm for single-space, 16.25cm for double-space
\geometry{textheight=22.5cm} % 22cm for single-space, 22.5cm for double-space

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H3N2_counts.png}
	\caption{\textbf{Sample counts through time and across regions.}
	This is a stacked bar plot, so that most months there are $\sim$100 total samples and $\sim$15 samples each from North America and from Europe.
	}
	\label{H3N2_counts}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H3N2_clades.png}
	\caption{\textbf{Frequency trajectories of H3N2 clades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2016.
	}
	\label{H3N2_clades}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.9\textwidth]{../figures/feb-2016/H3N2_3c2a_tree.png}
	\caption{\textbf{H3N2 / 3c2.a phylogeny colored by genotype.} 
	}
	\label{H3N2_3c2a_tree}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H3N2_mutations.png}
	\caption{\textbf{Frequency trajectories of 3c2.a subclades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2016.	
	}
	\label{H3N2_mutations}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H3N2_HI.png}
	\caption{\textbf{H3N2 phylogeny colored by antigenicity.}
	The left panel shows individual HI measurements of viruses against serum from A/HongKong/5738/2014.
	Cooler color indicates great antigenic similarity (less titer drop going from homologous to heterologous titers).
	The right panel shows model estimates of antigenic divergence from the root of the phylogeny.
	These estimates combine HI measurements from many different sera.
	Data is current through September 2015.
	}
	\label{H3N2_HI}
\end{figure}

@@

\begin{figure}[h!]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H3N2_basal_viruses.png}
	\caption{\textbf{Viruses basal to the (HA1:171K, HA2:77V/155E) clade (left panel) and to the HA1:142K/197R/168V clade (right panel).}
	Viruses are colored according to sampling region.
	}
	\label{H3N2_basal_viruses}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H1N1pdm_counts.png}
	\caption{\textbf{Sample counts through time and across regions.}
	This is a stacked bar plot, so that in good months there are $\sim$100 total samples and $\sim$15 samples each from North America and from Europe.	
	}
	\label{H1N1pdm_counts}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.9\textwidth]{../figures/feb-2016/H1N1pdm_tree.png}
	\caption{\textbf{H1N1pdm phylogeny colored by genotype.}
	}
	\label{H1N1pdm_tree}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H1N1pdm_mutations.png}
	\caption{\textbf{Frequency trajectories of H1N1pdm variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2016.	
	}
	\label{H1N1pdm_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H1N1pdm_6b2_tree.png}
	\caption{\textbf{H1N1pdm phylogeny showing clade 6b.2 viruses colored by sampling location.} 
	}
	\label{H1N1pdm_6b2_tree}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=1.0\textwidth]{../figures/feb-2016/H1N1pdm_HI.png}
	\caption{\textbf{H1N1pdm phylogeny colored by antigenicity.}
	The left panel shows individual HI measurements of viruses against serum from A/HongKong/5659/2012.
	Cooler color indicates great antigenic similarity (less titer drop going from homologous to heterologous titers).
	The right panel shows model estimates of antigenic divergence from the root of the phylogeny.
	These estimates combine HI measurements from many different sera.
	Data is current through September 2015.	
	}
	\label{H1N1pdm_HI}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Vic_mutations.png}
	\caption{\textbf{Frequency trajectories of B/Vic variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2016.	
	}
	\label{Vic_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Yam_clades.png}
	\caption{\textbf{Frequency trajectories of B/Yam clades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2016.	
	}
	\label{Yam_clades}
\end{figure}

@@

\begin{figure}[H]
	\centering		
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Yam_mutations.png}
	\caption{\textbf{Frequency trajectories of B/Yam variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2016.	
	}
	\label{Yam_mutations}
\end{figure}
